Turbulence in compact to giant H~II regions

### 2022-11-29 strucfunc_paper.tex
Write more on power law slopes
Still not finished

\subsubsection{The constancy of the power law slope}
\label{sec:constancy-power-law}
The slope \(m\) of the power-law portion of the structure function
shows no significant correlation with any other parameter
(see Table~\ref{tab:RestStats}),
with a weighted mean value of \(m = 1.01\).
The dispersion in fitted \(m\) values is 1.6 times higher than expected
on the basis of the confidence limits for the individual regions,
implying that there may be a real intrinsic dispersion of 0.17 in the slopes.
However, a \(\chi^2\) test shows that this is only marginally significant
(\(p = 0.11\)), so we cannot reject the idea that all the slopes are identical.

>>>>

\subsubsection{The constancy of the power law slope}
\label{sec:constancy-power-law}
The slope \(m\) of the power-law portion of the structure function
shows no significant correlation with any other parameter
(see Table~\ref{tab:RestStats}),
with a weighted mean value of \(m = 1.01\).
The dispersion in fitted \(m\) values is 1.6 times higher than expected
on the basis of the confidence limits for the individual regions,
implying that there may be a real intrinsic dispersion of \(\pm 0.17\) in the slopes.
However, a \(\chi^2\) test shows that this is only marginally significant
(\(p = 0.11\)), so we cannot rule out that all the slopes are identical.

\newcommand\DDD{\ensuremath{_{\mathrm{3D}}}}
For incompressible Kolmogorov turbulence,
the predicted slope of the three-dimensional structure function is \(m\DDD = 2/3\),
but intermittency and compressibility \citep{Schmidt:2008a}
can increase this to \(m\DDD \approx 0.8\) in the subsonic regime,
and up to \(m\DDD = 1\) in the supersonic regime.
Comparison with our measurements is complicated by projection smoothing,
which mean that \(m\DDD\) is only
observed directly for separations larger than the line-of-sight depth
of the emitting regions.
For smaller separations, one potentially observes a steeper slope:
\(m = m\DDD + 1 + \delta\kappa\),
where \(\delta\kappa\) represents the effects of emissivity fluctuations
along the line of sight \citep{Brunt:2004a},
and varies from \(\delta\kappa = 0\) in the incompressible limit
to \(\delta\kappa = -1\) in the case of strongly driven supersonic turbulence.

It is therefore not surprising that we see no significant correlation
between \(m\) and \(\sigma^2\pos\) 
(\(p = 0.33\), Table~\ref{tab:RestStats}).
Although theoretically one might expect a positive correlation of \(m\DDD\)
with the amplitude of the velocity fluctuations
due to the transition from subsonic
to supersonic turbulence \citep{Galtier:2011a},
this will be offset by a decrease in \(\delta\kappa\) 
if the amplitude of the density fluctuations
(and hence emissivity fluctuations) increases along
with the velocity fluctuations.

In figure

We also find no clear evidence for a broken power-law in any of our
structure functions, as has been suggested in previous studies.
Although in some regions we do observe a steepening at the smallest scales
(for example Figures~\ref{fig:strucfunc-fit-Galactic}a, \ref{fig:strucfunc-fit-MC}ab),
this can be accounted for in our model fits by
the spatial smoothing caused by atmospheric seeing.
This has a noticeable effect on the structure function at scales of
up to 5 times the FWHM of the seeing (Appendix~\ref{sec:effects-seeing-struc}).
There is a hint in the highest quality datasets that there may also be
a real steepening of the structure function at small scales
(see section~\ref{sec:sanity-check-derived}),
but higher spatial resolution observations are required in order to study this.

Theoretically, one might expect a positive correlation of the slope with the
amplitude of the velocity fluctuations, due to the transition from subsonic
to supersonic turbulence \citep{Galtier:2011a}.
However, the predicted change of slope is rather small,
\(\delta m \approx 0.2\)
\citep{Federrath:2021r},
and only one of our sources (30~Dor) is clearly in the supersonic regime,
so it is perhaps not surprising that we do not find a significant correlation
(\(p = 0.33\), Table~\ref{tab:RestStats}).
This is further complicated by the effect of projection along the line of sight

Theoretically, one might expect
